Towards a miniKanren with fair search strategies

### 2019-05-23 Paper/paper.tex
remove useless notes

\NOTE[LKC]{I change `1/4 in the answer' to `1/4 in the answer list'. }

@@

\NOTE[DPF]{I think that should be said as directly as in your note.}
\NOTE[LKC]{I state this fact at the beginning of this section.}
\NOTE[LKC]{We never use run* in this paper because fairness is only 
interesting when we have an unbounded number of answers. However, it is 
perfectly fine to use run* with any search strategies.}

@@

\NOTE[LKC]{I have rewritten this subsection.}

>>>>

@@

\NOTE[DPF]{I think that should be said as directly as in your note.}
\NOTE[LKC]{I state this fact at the beginning of this section.

``We never use run* in this paper because fairness is only 
interesting when we have an unbounded number of answers. However, it is 
perfectly fine to use run* with any search strategies.''}

@@
